Visual Question Answering with DeepProbLog

### 2022-03-09 paper/paper.tex
Add bibs

\section{INTRODUCTION}
The Neuro Symbolic AI community is growing rapidly, indicating that people start to recognize the value of the field. The Neuro Symbolic AI field is interested in building a bridge between the robustness of probabilistic knowledge, with the well-known popularity and proven strengths of deep neural networks. DeepProbLog offers this ability, by using both the strengths of neural networks (i.e. system 1, typical subconscious tasks such as visual recognition, the processing of languages, \dots), along with the strengths of rule-based probabilistic systems (i.e. system 2, slow, sequential thinking such as the derivation of a proof).

@@

\subsection{Presentation of the Text}

Papers submitted for publication to the Brazilian Power Electronics Journal should have, preferably, eight pages or less. Papers with a higher number of pages must pay an overlength page charge (R\$ 150 per extra page for SOBRAEP Member corresponding author or R\$ 200 per extra page for SOBRAEP Non-Member corresponding author) before its publication, until the limit of four extra pages. Consequently, the maximum page limit is 12 pages.
The Brazilian Power Electronics Journal is an open access journal, having the following publication fees: SOBRAEP Professional Member corresponding author – free; SOBRAEP Student Member corresponding author – R\$ 50 per paper; SOBRAEP Non-Member corresponding author – R\$ 200 per paper.

Authors must use International System units (SI or MKS).

Authors of the paper must prepare it and then send it as a PDF file, through the https://mc04.manuscriptcentral.com/revistaep, in accordance with these guidelines. The manuscripts that do not follow these guidelines will be rejected, and the authors will be informed.

\subsection{Text Editing}
The manuscript must be prepared on A4 page format \linebreak (297 mm x 210 mm), as demonstrated in these guidelines.

The recommended word processor is Word for Windows.

\subsubsection{Type sizes} The type sizes specified in these guidelines are according to the word processor Word for Windows and the typeface must be Times New Roman. Table I shows the standard sizes of the characters that should be used in the different sections of the manuscript.

\subsubsection{Page Format} Set top and bottom margins to 25 mm, left margin to 18 mm and right margin to 12 mm.~The column is \linebreak 87 mm. The space between the two columns is 6 mm. Paragraph indentation is 4mm.

%Body Text
\begin{table}[H]
	\centering
	\caption{\textbf{Type Sizes}}
	\footnotesize
	\setlength{\tabcolsep}{5pt}
	\begin{tabular}{cccc}
		\toprule [1.3pt]	
		\multicolumn{4}{c}{ \textbf{Style} } \\
		\hline
		\multirow{2}{1.1cm}{\centering \textbf{Size (Points)}} & \multirow{2}{*}{\textbf{Normal}} &
		\multirow{2}{*}{\textbf{Bold}} & \multirow{2}{*}{\textbf{Italic}} \\
		&  &  & \\		
		\hline
		8 & Table texts &  &  \\
		\hline
		9 &  Figure captions  &  &  \\
		\hline
		\multirow{3}{*}{10} &
		\multirow{3}{2cm}{\centering Authors' affiliations; main text; references}  &
		\multirow{3}{2cm}{\centering Abstract text; keywords, table captions} &
		\multirow{3}{2.1cm}{\centering Abstract title and keywords title} \\
		& &  &  \\
		& &  &  \\
		\hline
		12 & Authors' names & &  \\
		\hline
		14 &  & Paper title & \vspace*{-0.8mm}\\
		\bottomrule[1.3pt]
	\end{tabular} \label{table:TableI}
\end{table}

\section{ORGANIZATION OF THE PAPER}

@@

\bibliographystyle{bib_sobraep}
\bibliography{ref_sobraep}

@@

\section*{BIOGRAPHIES}
\noindent\textbf{\underline{John Doe}}, born in 02/30/1960 in Somewhere is an electrical engineer (1983), master (1985) and doctor in Electrical Engineer (1990) with the University of Y.

Between 1990 and 1995 he was the coordinator of Laboratory X. He is currently a full professor at University of Y. His areas of interest are: power electronics, electricity conversion quality, electronic control systems and electrical machine actuation.

Dr. Doe is member of the SOBRAEP, SBA and IEEE. Between 1998 and 2000, he was editor of the Brazilian \linebreak Power Electronics Journal.

>>>>

\section{INTRODUCTION}
The Neuro Symbolic AI community is growing rapidly, indicating that people start to recognize the value of the field. The Neuro Symbolic AI field is interested in building a bridge between the robustness of probabilistic knowledge, with the well-known popularity and proven strengths of deep neural networks. DeepProbLog \cite{deepproblog} offers this ability, by using both the strengths of neural networks (i.e. system 1, typical subconscious tasks such as visual recognition, the processing of languages, \dots), along with the strengths of rule-based probabilistic systems (i.e. system 2, slow, sequential thinking such as the derivation of a proof).

@@

\section{ORGANIZATION OF THE PAPER}
%TODO

@@

\bibliographystyle{bib_sobraep}
\bibliography{Capita_Selecta_AI_Initial_Idea}

@@
